---
title: "Pair-wise statistical comparisons"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Pair-wise statistical comparisons}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 10,
  fig.height = 8,
  message = FALSE,
  warning = FALSE
)
```

# Libraries

```{r setup}
library(regionaldrivers)
library(magrittr)
```

# Data loading

`SSCT_data` and `SSCT_labelled_data` are loaded with the package.
Here is what 10 random rows of each looks like:

```{r data loading1, echo = FALSE}
SSCT_labelled_data %>% dplyr::sample_n(10) %>%
	knitr::kable(digits = 3, format = "html", caption = "SSCT_labelled_data") %>% 
	kableExtra::kable_styling(bootstrap_options = c("hover", "condensed")) %>% 
	kableExtra::scroll_box(width = "7in", height = "5in")
```

```{r data loading2, echo = FALSE}	
SSCT_data %>% dplyr::sample_n(10) %>%
	knitr::kable(digits = 3, format = "html", caption = "SSCT_data") %>% 
	kableExtra::kable_styling(bootstrap_options = c("hover", "condensed")) %>% 
	kableExtra::scroll_box(width = "7in", height = "5in")	
```

# Data transformation

We transform the data to retain what we need for the analysis:

```{r melting}
drivers_data <- cbind(SSCT_labelled_data, SSCT_data) %>%
	dplyr::select(c("CONFINEMEN", "layer_sd.rstr", "H.960", "SLOPE", "RUSLE", "ward"))	%>%
	dplyr::rename(ward.grp = ward) %>%
	reshape2::melt(id.vars = "ward.grp")
head(drivers_data)
```

# Statistical testing and visualization

We can now visualize the results from a pair-wise statistical comparison with `significative_diff_boxplot()`.

## Box plots

```{r viz box plots}
Dunn_results <- significative_diff_boxplot(drivers_data, type = "Dunn", padjmeth = "bonferroni")
Dunn_results$p
```

## Matrices

As the boxplots might be difficult to read, the p-value can be recasted into a matrix form with `plot_pairwise_pvalue()`.

```{r}
plotly::ggplotly(
	plot_pairwise_pvalue(Dunn_results$stats),
	tooltip = c("group1", "group2", "p.value")
)	
```

# Lollipop charts

We can repeat the above procedure for all data and visualize the results at the number of significant pairwise comparisons.
This time we select most data, removing the data with near-zero variance and the Indices of Catchment Integrity.
`significative_count_lollipop()` produces a lollipop chart counting the number of significant pairwise comparison.
If `normalize = TRUE`, the counts are normalized by the number of pairwise comparisons.

```{r lollipop, echo = TRUE}
all_drivers_data <- cbind(SSCT_labelled_data, SSCT_data) %>%
	dplyr::select(-head(colnames(SSCT_data), -1)) %>%
	dplyr::select(-caret::nearZeroVar(., names = TRUE)) %>%
	dplyr::select(-c("CHYD", "CCHEM", "CSED", "CCONN", "CTEMP", "CHABT", "ICI", "WHYD", "WCHEM", "WSED", "WCONN", "WTEMP", "WHABT")) %>%
	dplyr::rename(ward.grp = ward) %>%
	reshape2::melt(id.vars = "ward.grp") %>%
	na.omit()
Dunn_results <- significative_diff_boxplot(all_drivers_data, type = "Dunn", padjmeth = "bonferroni")
significative_count_lollipop(Dunn_results)$p %>% plotly::ggplotly() 
significative_count_lollipop(Dunn_results, normalize = TRUE)$p %>% plotly::ggplotly()
```