---
title: "Feature importance"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Feature importance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.height = 8,
  message = FALSE,
  warning = FALSE
)
```

# Libraries

```{r setup}
library(regionaldrivers)
library(magrittr)
```

# Data loading

`SSCT_data` and `SSCT_labelled_data` are loaded with the package.
Here is what 10 random rows of each looks like:

```{r data loading1, echo = FALSE}
SSCT_labelled_data %>% dplyr::sample_n(10) %>%
	knitr::kable(digits = 3, format = "html", caption = "SSCT_labelled_data") %>% 
	kableExtra::kable_styling(bootstrap_options = c("hover", "condensed")) %>% 
	kableExtra::scroll_box(width = "7in", height = "5in")
```

```{r data loading2, echo = FALSE}	
SSCT_data %>% dplyr::sample_n(10) %>%
	knitr::kable(digits = 3, format = "html", caption = "SSCT_data") %>% 
	kableExtra::kable_styling(bootstrap_options = c("hover", "condensed")) %>% 
	kableExtra::scroll_box(width = "7in", height = "5in")	
```

# Data transformation

We transform the data to retain what we need for the analysis.

```{r data selection}
drivers_data <- cbind(SSCT_labelled_data, SSCT_data) %>%
  dplyr::select(-c("SiteID", "POINT_X", "POINT_X"))
```

# Feature importance

The function `feature_importance()` derives the feature importance from `drivers_data` and the name of the target column, here `ward`.
The `method` argument accepts [filter methods](https://mlr.mlr-org.com/articles/tutorial/filter_methods.html) from `mlr`.
The function resamples the dataset `iters` time, for this vignette, the number of iterations was lowered to 10 from the default value of 500.

```{r feature importance}
varimp <- feature_importance(
  drivers_data, "ward", 
  methods = c("kruskal.test", "FSelectorRcpp_information.gain", "FSelector_chi.squared", "randomForest_importance"),
  .iters = 10,
  .first = 10)
varimp$p
```
